Supplementary Information

### 2021-08-26 doc/manuscript/ForestGEO_treerings.Rmd
Lutz fixes
#144

```{r eval=FALSE, echo=FALSE}
# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @vlam_temperature_2014; @maxwell_declining_2016; @sniderhan_growth_2016; @alfaro-sanchez_growth_2017;@bourg_initial_2013; @helcoski_growing_2019 @gonzalez-akre_scbi-forestgeoscbi-forestgeo-data_2020-1; @bumann_assessing_2019; @samonil_individual-based_2013;  @alexander_potential_2019; @finzi_carbon_2020; @birch_birch_2020; @birch_birch_2020b; @birch_birch_2020c; @birch_birch_2020d; @dye_comparing_2016
---

>>>>

```{r eval=FALSE, echo=FALSE}
# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @vlam_temperature_2014; @maxwell_declining_2016; @sniderhan_growth_2016; @alfaro-sanchez_growth_2017;@bourg_initial_2013; @helcoski_growing_2019 @gonzalez-akre_scbi-forestgeoscbi-forestgeo-data_2020-1; @bumann_assessing_2019; @samonil_individual-based_2013;  @alexander_potential_2019; @finzi_carbon_2020; @birch_birch_2020; @birch_birch_2020a; @birch_birch_2020b; @birch_birch_2020c; @dye_comparing_2016
---
